---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# greta.distributions

<!-- badges: start -->
<!-- once you've signed into travis and set it to wath your new repository, you can edit the following badges to point to your repo -->
[![Codecov test coverage](https://codecov.io/gh/greta-dev/greta.distributions/branch/master/graph/badge.svg)](https://codecov.io/gh/greta-dev/greta.distributions?branch=master)
[![R-CMD-check](https://github.com/njtierney/greta.distributions/workflows/R-CMD-check/badge.svg)](https://github.com/njtierney/greta.distributions/actions)
<!-- badges: end -->

# Why 

This package exists for two reasons:

1. Provide extra distributions to use alongside the  [`greta`](https://greta-stats.org/) programming interface for creating  statistical models.
2. Provide helper functions for creating new distributions

## Example extra distributions

### Zero Inflated Negative Binomial

### Zero Inflated Poisson

## Helpers for adding extra distributions

# Installation

You can install `greta.distributions` from github with:

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("greta-dev/greta.distributions")
```

